\section{Experience}

\begin{adcvtabletwo}
  \adcvrowtwo{\textbf{Post-Doctoral Researcher}, \href{https://www.cnrs.fr/fr}{CNRS}, Paris, France}{2023--}
  \ifextended%
    \adcvrowmulti{
      During this postdoc I will work on the \href{https://github.com/lucanest/Phyloformer}{phyhloformer} project with \href{https://scholar.google.com/citations?user=54bOCmQAAAAJ\&hl=en\&oi=ao}{Laurent Jacob} and members of the LBBE in Lyon. I am working on improving performance of the model as well as it's generalisation. Extensions to the model are planned, such as taking unaligned sequences as input and including a differentiable tree-building step in an end-to-end pipeline. 
    }
  \else
    \adcvrowmulti{Improve the accuracy of predicted distances and develop the architecture of the model to accept unaligned sequences as input for the \href{https://github.com/lucanest/Phyloformer}{phyhloformer} project. Work with \href{https://scholar.google.com/citations?user=54bOCmQAAAAJ\&hl=en\&oi=ao}{Laurent Jacob}.}
  \fi

  \adcvrowskip%

  \adcvrowtwo{\textbf{PhD Student}, \href{https://www.pasteur.fr/en}{Institut Pasteur}, Paris, France}{2020--2023}
  \ifextended%
    \adcvrowmulti{
      PhD in computational biology, focused on improving and learning from sequence alignments. With the ever growing quantity of high quality sequencing data, we are now able to develop methods to take advantage of this data. My PhD project followed 2 different axes: (1) Using machine learning to discover Drug resistance mutations in HIV (Continuation of the M.Sc project) (2) Search of a function space for sequence transformation functions that improve sequence mapping and alignment.
    }
    \adcvrowmulti{This PhD was supervized by \href{http://rayan.chikhi.name/}{Rayan Chikhi} and funded by the \href{https://prairie-institute.fr/chairs/blassel-luc/}{PRAIRIE} institute. The manuscript can be found \href{https://thesis.lucblassel.com}{here}}
  \else
    \adcvrowmulti{PhD in computational biology, focused on improving and learning from sequence alignments.}
    \adcvrowmulti{Funded by \href{https://prairie-institute.fr/chairs/blassel-luc/}{PRAIRIE} and supervized by \href{http://rayan.chikhi.name/}{Rayan Chikhi}. Manuscript \href{https://thesis.lucblassel.com}{here}.}
  \fi

  \adcvrowskip%

  \adcvrowtwo{\textbf{Research Engineer}, \href{https://www.pasteur.fr/en}{Institut Pasteur}, Paris, France}{2018--2020}
  \ifextended%
    \adcvrowmulti{Using machine learning and large datasets to explore the drug resistance landscape in HIV.\@ Supervized by \href{https://prairie-institute.fr/chairs/gascuel-olivier/}{Olivier Gascuel}. A large dataset of UK HIV sequences associated with patient RT-treatment status was used to train several machine learning algorithms. Examining the importatnt learned features gave us insight in mutations associated to ART failure. This project resulted in a \hyperref[sec:publications]{publication}. }
    \adcvrowmulti{Project page \href{https://research.pasteur.fr/en/project/drm-hiv/}{here}, and \href{https://lucblassel.com/files/msc-thesis-french.pdf}{M.Sc thesis} (in french).}
  \else
    \adcvrowmulti{Using machine learning and large datasets to explore the drug resistance landscape in HIV.}
    \adcvrowmulti{Supervized by \href{https://prairie-institute.fr/chairs/gascuel-olivier/}{Olivier Gascuel}. Project page \href{https://research.pasteur.fr/en/project/drm-hiv/}{here}.}
  \fi

  \adcvrowskip%

  \adcvrowtwo{\textbf{Data Scientist Intern}, \href{https://www.capitaldata.fr/}{CapitalData}, Paris, France}{Mar-Sept 2017}
  \ifextended%
    \adcvrowmulti{As a data scientist intern at Capital data I was tasked with developing a software pipeline to validate data prior to database integration, and detect anomalies usign time series. This was implemented in R and Python. I also, developed reporting-oriented data visualizations of KPIs using BIME and Tableau. Finally statistical AB-testing was also done using python.}
  \else
    \adcvrowmulti{Development of automated data validation and anomaly detection pipelines using R, Golang and Python.}
  \fi

  \adcvrowskip%

  \adcvrowtwo{\textbf{Teaching and tutoring}, self-employed, Paris, France}{2015--2022}
  \ifextended%
    \adcvrowmulti{Since the beginning of my higher education, I have beedn tutoring middle school, high school and university students in scientific subjects, mainly mathematics. The aim is to turn the students into independents people, more confident in their abilities and more knowledgeable in order to excel in their respective studies.}
    \adcvrowmulti{Since Septemeber 2021, I have been doing oral examination in English for PCSI preparatory class students as the \href{http://pirandello.org/index.php/nos-formations/cpge/pcsi-physique-chimie-sciences-de-l-ingenieur}{ENCPB} in Paris, France.}
  \else
    \adcvrowmulti{Tutoring in English, mathematics, biology, physics, chemistry and computer science. From middle school to university level. Weekly English oral examinations at the \href{http://pirandello.org/index.php/nos-formations/cpge/pcsi-physique-chimie-sciences-de-l-ingenieur}{ENCPB} since Sept. 2021.}
  \fi

\end{adcvtabletwo}
